Understanding the problem

### 2024-04-17 presentations/understanding the problem.qmd
more examples

```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example4.R")
example4
```
---

However, this result is area sensitive

```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example5.R")
example5
```

---
Next, variables aggregated at EAA scale

>>>>

```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example4.R")
example4
```

Adding area weighting to the first example
```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example3b.R")
example3b
```

and to the second example
```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example5.R")
example5
```

Next, variables aggregated at EAA scale by taking the area weighted mean. When would this make sense to do? Obviously not for count variables.

```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example6.R")
example6
```

Here, variable aggregated at EAA scale with no area weighting

```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example7.R")
example7
```
